Active Learning for SAT Solver Benchmarking

### 2023-01-24 paper/paper.tex
3.1 model

Algorithm~\ref{algALBenchmark} outlines our benchmarking framework. 
Given a set of solvers~$\mathcal{A}$, instances~$\mathcal{I}$ and runtimes~$r$, we first initialize a prediction model~$\mathcal{M}$ for the new solver $\hat a$ (Line~1).
The prediction model~$\mathcal{M}$ is used to repeatedly select an instance (Line~4) for benchmarking $\hat a$ (Line~5). 
The acquired result is subsequently used to update the prediction model~$\mathcal{M}$ (Line~7). 
When the stopping criterion is met (Line~3), we quit the benchmarking loop and predict the final score of $\hat a$ (Line~8). 
Algorithm~\ref{algALBenchmark} returns the predicted score of $\hat a$ as well as the acquired instances and runtime measurements (Line~9).

@@

Let SAT solvers $\mathcal{A}$, benchmark instances $\mathcal{I}$, and runtimes $r : \mathcal{A} \times \mathcal{I} \rightarrow \left[0, \tau\right]$ be given.
We denote the new solver to be ranked by $\hat a \not\in \mathcal{A}$ and define $\mathcal{\hat A} := \mathcal{A} \cup \lbrace \hat a \rbrace$ to denote all solvers, including the new one.
Model initialization (Line~1) creates the prediction model and transforms runtimes, as discussed later.
No model training is needed at this point since we do not have any labeled data yet.
Later, model $\mathcal{M}$ provides a runtime-label prediction function $f : \mathcal{\hat A} \times \mathcal{I} \rightarrow \mathbb{R}$ that powers the decisions within our framework.
In particular, the model update (Line~7) uses all acquired runtimes to train $f$ with a standard supervised machine-learning methodology.
Model training uses instance features and known runtimes~$r$.
The transformed runtime observations~$\mathcal{R}$ serve as ground-truth labels.
Note that we build a new prediction model in each iteration since running experiments (Line~5) dominates the runtime of model training by magnitudes.
Finally, we predict the score of the new solver $\hat a$ with the prediction function~$f$ (Line~8).

@@

\subsection{Data}

>>>>

Algorithm~\ref{algALBenchmark} outlines our benchmarking framework. 
Given a set of solvers~$\mathcal{A}$, instances~$\mathcal{I}$ and runtimes~$r$, we first initialize a prediction model~$\mathcal{M}$ for the new solver $\hat a \not\in \mathcal{A}$ (Line~1).
The prediction model~$\mathcal{M}$ is used to repeatedly select an instance (Line~4) for benchmarking $\hat a$ (Line~5). 
The acquired result is subsequently used to update the prediction model~$\mathcal{M}$ (Line~7). 
When the stopping criterion is met (Line~3), we quit the benchmarking loop and predict the final score of $\hat a$ (Line~8). 
Algorithm~\ref{algALBenchmark} returns the predicted score of $\hat a$ as well as the acquired instances and runtime measurements (Line~9).

@@

The model $M$ maintains runtime transformations which we describe in the subsequent section. 
Additionally, $M$ provides a runtime-label prediction function $f : \mathcal{\hat A} \times \mathcal{I} \rightarrow \mathbb{R}$ for all solvers $\mathcal{\hat A} := \mathcal{A} \cup \lbrace \hat a \rbrace$.
The prediction function $f$ powers instance selection as described in Section~\ref{sec:main:selection}.
During model update (Algorithm~\ref{algALBenchmark},~Line~7), $f$ is trained to predict the known and acquired transformed runtimes based on instance features described in Section~\ref{sec:exdesign:data}.
Note that we build a new prediction model in each iteration since running experiments (Line~5) dominates the runtime of model training by magnitudes.
Finally, we predict the score of the new solver $\hat a$ with the prediction function~$f$ (Line~8).

@@

\subsection{Data}
\label{sec:exdesign:data}
